Project-I by Group CITYNAME

### 2015-10-31 report/paper.tex
Last changes to the report

For our first attempt at predicting the data, we simply used the initial
features and used kFold with $k=4$ to display the evolution of the RMSE as a
function of the regularizing lambda both for the training and test data. 
The lambda we used ranged from $10^{-4}$ to
$10^3$, with 500 points. The results of the ridge regression are already
satisfactory, with an error of approximately $0.32\pm0.005$ on the training set
and $0.34\pm0.005$ on the test set, that is approximately one third of the
variance of the output variable.

@@

As expected, both training error and test error decrease as the proportion of
training data increases. The test error obtained seems to exhibit a quit
satisfactory behaviour.

@@

>>>>

For our first attempt at predicting the data, we simply used the initial
features and used kFold with $k=4$ to display the evolution of the RMSE as a
function of the regularizing lambda both for the training and test data. 
The lambda we used ranged from $10^{-4}$ to
$10^3$, with 500 points. The results of the ridge regression are already
satisfactory, with an error of approximately $0.32\pm0.005$ on the training set
and $0.34\pm0.005$ on the test set, that is approximately one third of the
standard deviation of the output variable.

@@

As expected, both training error and test error decrease as the proportion of
training data increases. The test error obtained seems to exhibit a quite
satisfactory behaviour.

@@

\subsection{Regression Summary}
While simple ridge regression with an appropriately optimized lambda already
gave decent results on our dataset, we obtained better results using polynomial
transformations of well chosen features. Doing so, we obtain an error that is
approximately one fifth of the standard deviation.
